---
title: "Wine Quality Prediction"
output: html_notebook
---
- predict the quality of a wine based on the chemical properties of the wine.
- dataset: wine quality dataset hosted on the <a href="https://archive.ics.uci.edu/ml/datasets/Wine+Quality">UCI website</a>. 
- classify white wine rating.

load white wine dataset
```{r,message=F}
library(tidyverse)
wine = read.csv('./data/winequality-white.csv',sep=';')
head(wine)
```
how does the quality of wine distribute?
```{r}
ggplot(wine,aes(quality)) + geom_histogram(binwidth = 1)+
    stat_bin(aes(y=..count.., label=..count..), geom="text", vjust=-.5,binwidth = 1) 
```
Most white wines has rating of 6. distribution is quite normal with a little skew toward lower rating. 

assign good (1) to rating >=7, bad(0) to rating <=6
```{r}
wine$quality = ifelse(wine$quality >6, 'g','b')
ggplot(wine, aes(quality))+geom_bar()
```

train random forest model
```{r}
library(caret)
set.seed(2018)
myControl <- trainControl(
  method = "cv",
  number = 5,  
  summaryFunction = twoClassSummary,
  classProbs = TRUE, 
  verboseIter = TRUE)
model <- train(quality~., data=wine, method='ranger', trControl=myControl)

```
```{r}
print(model)
```

